Short Paper

### 2023-04-05 manuscript/manuscript.qmd
Fix YAML
Finalise complete reference list

---
title: Short Paper
subtitle: A Short Subtitle
author:
 - name: Alice Anonymous
  email: alice@example.com
  affiliations: 
    - id: some-tech
     name: Some Institute of Technology
     department: Department Name
     address: Street Address
     city: City
     state: State
     postal-code: Postal Code
  attributes:
    corresponding: true
  note: This is the first author footnote.
 - name: Bob Security
  email: bob@example.com
  affiliations:
    - id: another-u
     name: Another University
     department: Department Name
     address: Street Address
     city: City
     state: State
     postal-code: Postal Code
  note: |
   Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
 - name: Cat Memes
  email: cat@example.com
  affiliations:
    - ref: another-u
  note: Yet another author footnote.
 - name: Derek Zoolander
  email: derek@example.com
  affilations:
    - ref: some-tech
abstract: |
 This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
 - keyword1
 - keyword2
date: last-modified
bibliography: [bibliography.bib, introduction.bib, man-qech-air-quality.bib]
format:
 elsevier-pdf:
  keep-tex: true
  journal:
   name: Habitat International
   formatting: review
   model: 3p
   cite-style: authoryear
   highlights:
    - Highlight 1
    - Highlight 2
    - Highlight 3
editor: 
 markdown: 
  wrap: 72
---

@@

```{r}
# Table 1. Particulate matter targets from @worldhealthorganization2021who
knitr::include_graphics(here::here("img/image-replace-table.png"))

>>>>

---
title: Short Paper
subtitle: A Short Subtitle
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliations: 
        - id: some-tech
          name: Some Institute of Technology
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    attributes:
        corresponding: true
    note: This is the first author footnote.
  - name: Bob Security
    email: bob@example.com
    affiliations:
        - id: another-u
          name: Another University
          department: Department Name
          address: Street Address
          city: City
          state: State
          postal-code: Postal Code
    note: |
      Another author footnote, this is a very long footnote and it should be a really long footnote. But this footnote is not yet sufficiently long enough to make two lines of footnote text.
  - name: Cat Memes
    email: cat@example.com
    affiliations:
        - ref: another-u
    note: Yet another author footnote.
  - name: Derek Zoolander
    email: derek@example.com
    affilations:
        - ref: some-tech
abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae. Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography: man-qechairquality.bib
format:
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Habitat International
      formatting: review
      model: 3p
      cite-style: authoryear
      highlights:
        - Highlight 1
        - Highlight 2
        - Highlight 3
editor: 
  markdown: 
    wrap: 72
---

@@

```{r}
# Table 1. Particulate matter targets from @worldhealthorganization2021who
knitr::include_graphics(here::here("manuscript/img/image-replace-table.png"))
